---
title: "Homework #1 -- Pet Names Dataset"
author: "Amsha Fisal "
date: 
output: github_document
---

**Student ID:2201000180**

**Deadline:** 23:59 on Saturday, 13 February 2021

**Total Points:** 30


## Loading Packages

```{r load-packages, message = FALSE}

library(tidyverse)
library(openintro)
library(ggrepel)
```


##Exercises

#Answer Exercise1
`1. 52519

(4 points)
```{r}

```
#Answer Exercise2

`2. 7 variables

(4 points)

```{r}

```
#Answer Exercise3
1-Dog
2-Cat
3-Goat

`3.seattlepets%>%count(animal_name, sort = TRUE)
seattlepets%>%count(species, sort = TRUE)

(4 points)

```{r}

```
#Answe Exe4
Top 5 names for Dog
Lucy        
Charlie       
Bella         
Luna          
Daisy
Top 5 names for Cats
NA
Luna
Lucy
Lily
Max
(10 points)

```{r species-name-top5, eval=TRUE}

```
#ANSWER Exe5
`5.  What names are more common for cats than dogs? The ones above the line or the ones below the line?

lily
milo
charli
bella
luna
lala
stella
max
molly
maggie
jack
henry
pepper


(4 points)

`6. Is the relationship between the two variables (proportion of cats with a given name and proportion of dogs with a given name) positive or negative? What does this mean in context of the data?

positive, whenever increased name for dogs. increased name cat

(4 points)